Machine Learning Methods for Site-specific Input Management

### 2022-03-18 Codes/PrepareResults.rmd
Edits by TM on many fronts.

theme_dist <- 
  theme_bw()+
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom",
    text  = element_text(family = "Times New Roman")
    )

@@

```{r}
#/*--------------------------------*/
#' ## Preparation
#/*--------------------------------*/
# --- MB function --- #
gen_yield_MB <- function(ymax, alpha, beta, N) {
  yield <- ymax * (1 - exp(alpha + beta * N))
  return(yield)
}

# --- extract sites that have wide range of true optimal N --- #
get_rows_optN <- function(data, value, range) {
  res <- data %>%
    .[opt_N %between% c(quantile(opt_N, prob = value - range), quantile(opt_N, prob = value + range))
    ] %>%
    .[,group := value]
}

prep_coef_dt <- 
  field_cell_sf %>%
  data.table() %>%
  .[sim==1,.(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]

@@

coef_dt <- 
  lapply(
    c(0.01, 0.25, 0.5, 0.75, 0.99), 
    function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
  bind_rows() %>%
  # --- select one site from each group --- #
  .[,.SD[sample(.N, size = 1)], by = group]

seq_N <- 
  seq(min(coef_dt[,opt_N]) -50, max(coef_dt[,opt_N])+100, by=1) %>%
  round()

res_y_dt <-  
  coef_dt %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = group] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield*(1 + m_error)] %>%
  .[, opt_N := round(opt_N)] %>%
  melt(id.vars = c("group", "N", "opt_N"), measure.vars = c("det_yield", "yield")) %>%
  .[, variable := case_when(
    variable == "det_yield" ~ "Yield",
    variable == "yield" ~ "Yield including errors"
  )] %>%
  .[,group := case_when(
    group == 0.01 ~ "site 1",
    group == 0.25 ~ "site 2",
    group == 0.5 ~ "site 3",
    group == 0.75 ~ "site 4",
    group == 0.99 ~ "site 5"
    )]

#/*--------------------------------*/
#' ## Visualization
#/*--------------------------------*/
sub_dt <- res_y_dt[variable=="Yield" & N == opt_N]

# --- MB function to N --- #
vis_MB_curve <- 
  ggplot(res_y_dt[variable=="Yield"]) +
    geom_line(
      aes(x=N, y=value, group=factor(group))
    ) +
    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
    # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
    scale_alpha_manual(
      name = NULL,
      values = 1,
      breaks = "Yield at EONR",
      guide = guide_legend(override.aes = list(linetype = 0,
        shape = 16,
        color = "red")
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

```{r}
# /*===========================================*/
#'=  Prepare illustrative yield response curve estimated by RF =
# /*===========================================*/

#/*--------------------------------*/
#' ## Preparation
#/*--------------------------------*/
# --- ML functions --- #
library(grf)
source(here("GitControlled/Codes/0_2_functions_main_sim.R"))

@@

# /*===== Train ML =====*/
temp_var_ls <- c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")

@@

# === Yield prediction === #
# --- All N experimental rates --- #
N_rate <- test_dt[,aa_n] %>% unique() %>% sort()
# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
tg_N_rate <- N_rate[c(2,3,4)]

# --- for true yield response function --- #
seq_N <- 
  seq(min(N_rate) -30, max(N_rate)+30, by=1)
# seq_N <- 
#   seq(min(N_rate), max(N_rate), by=1)

res_true <- 
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = unique_subplot_id] %>%
  .[,det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[,yield := det_yield*(1 + m_error)]

# --- for predicted yield at five experimental N rates --- #
res_pred <- 
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)),] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  .[,RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[,BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))

find_examples_main  <- 
  res_pred %>%
  .[variable == "BRF" & aa_n==N,] %>%
  .[, y_diff_brf := abs(yield - value)] %>%
  .[y_diff_brf < 500, unique_subplot_id]
  # .[y_diff_brf < 500 & y_diff_brf < 1000, unique_subplot_id]

@@

vis_res_true <- 
  res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[,site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
    )]

vis_res_pred <- 
  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[,site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
    )]

vis_MB_BRF_y <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, group = site)
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=value, group = site, alpha = "Predicts"), shape=2, size = 1.5
    ) +
    # --- Yield at applied N rate --- #
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 1.5) +
    facet_wrap(~variable) +
    scale_alpha_manual(
      name = NULL,
      values = c(1, 1),
      breaks = c("Predicts", "True yield at actual N rate that was applied"),
      guide = guide_legend(override.aes = list(linetype = c(0, 1),
        shape = c(2, 16),
        color = c("black", "blue")) 
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(-0.5, format(0), 12000, format(0)),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(0.02, format(1, nsmall = 1), 2000000, 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sub(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sub(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sub(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 3, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 3, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"),")."),
    ref_symbols = NA
  ) %>%
  # set_caption(
  #   caption = "Table C.1: The parameters for the Variogram models",
  #   style = "Table Caption"
  # ) %>%
  autofit()
```

@@

one_subplot <- ex_subplots[3,]

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <- 
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("4 \u00D7 1 subplots") +
  theme_figure

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2,], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("6 \u00D7 6 cells") +
  theme_figure

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE)+
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7) + 
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8+0.2, ymin = 0.382, ymax = 0.382 +0.2) +
  #/*----------------------------------*/
  #' ## Add braces
  #/*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43,0.43+0.1), c(0.372-0.004, 0.645+0.013)), color ="red", rotate = 270, inherit.data=F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401-0.002, 0.529 +0.011)), color ="red", rotate = 270, inherit.data=F) +
  #/*----------------------------------*/
  #' ## add annotations
  #/*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family="Times New Roman") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family="Times New Roman") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
    arrow = arrow(length = unit(0.1, "cm")), size=0.5) +
  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family="Times New Roman") +
  theme_void()
```

@@

```{r, dependson = "setup"}
# === alpha map === #
field_alpha <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = alpha), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(1) " ~alpha)) +
  theme(legend.title = element_blank()) +
  theme_figure

# === beta map === #
field_beta <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = beta), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(2) " ~beta)) +
  theme(legend.title = element_blank()) +
  theme_figure

@@

# === m_error map === #
field_m_error <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression(paste("(4) " ~epsilon, " (kg/ha)"))) +
  theme(legend.title = element_blank()) +
  theme_figure

@@

```{r}
vis_RMSE_y_eonr <- 
  res_y_test %>%
  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  guides(
    fill = guide_legend(override.aes=list(shape=21))
  ) +
  labs(fill="Simulation Round", shape="Method") +
  # guides(fill = "none") +
  # facet_wrap( ~ Model, ncol = 2) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist 
```

@@

# === Function for RMSE Calculation === #
rmse_general <-function(preds,actual){ 
  sqrt(mean((actual - preds)^2)) %>%
  round(.,1) %>%
  format(, nsmall = 1)
}

rmse <- sample_simRes_test_y %>%
  .[, .(
    rmse_y_det = rmse_general(pred_yield, det_yield),
    rmse_y = rmse_general(pred_yield, yield)
    ), by= .(Method, Model)]

rmse <- sample_simRes_test_y %>%
  .[, .(
    rmse_y_det = paste0("RMSE = " ,rmse_general(pred_yield, det_yield)),
    rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
    ), by= .(Method, Model)]

vis_y_pred <- ggplot(sample_simRes_test_y) +
  geom_point(aes(x=det_yield, y=pred_yield), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  geom_text(data=rmse, aes(x=-Inf,y=+Inf,label=rmse_y_det),
              hjust = -0.1,  vjust = 3, size=3.5, family = "Times New Roman") +
  facet_grid(Model ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Predicted Yield (kg/ha)") +
  labs(x = "True Yield without error (kg/ha)") +
  theme_dist
```

@@

```{r, dependson = "source-results"}
#/*----------------------------------*/
#' ## Distribution of RMSE of EONR estimates
#/*----------------------------------*/
plot_dis_optN <-
  allML_summary_bySim %>%
  .[type=="test",] %>%
  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
  facet_wrap(~Model, ncol = 1) +
  labs(x = "RMSE (kg/ha)") +
  theme_dist

>>>>

theme_dist <-
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom",
    text = element_text(family = "Times New Roman")
  )

@@

```{r}
# /*--------------------------------*/
#' ## Preparation
# /*--------------------------------*/
# --- MB function --- #
gen_yield_MB <- function(ymax, alpha, beta, N) {
  yield <- ymax * (1 - exp(alpha + beta * N))
  return(yield)
}

# --- extract sites that have wide range of true optimal N --- #
get_rows_optN <- function(data, value, range) {
  res <- data %>%
    .[opt_N %between% c(quantile(opt_N, prob = value - range), quantile(opt_N, prob = value + range))] %>%
    .[, group := value]
}

prep_coef_dt <-
  field_cell_sf %>%
  data.table() %>%
  .[sim == 1, .(unique_cell_id, opt_N, alpha, beta, ymax, m_error)]

@@

coef_dt <-
  lapply(
    c(0.01, 0.25, 0.5, 0.75, 0.99),
    function(x) get_rows_optN(data = prep_coef_dt, value = x, range = .0005)
  ) %>%
  bind_rows() %>%
  # --- select one site from each group --- #
  .[, .SD[sample(.N, size = 1)], by = group]

seq_N <-
  seq(min(coef_dt[, opt_N]) - 50, max(coef_dt[, opt_N]) + 100, by = 1) %>%
  round()

res_y_dt <-
  coef_dt %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = group] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield * (1 + m_error)] %>%
  .[, opt_N := round(opt_N)] %>%
  melt(id.vars = c("group", "N", "opt_N"), measure.vars = c("det_yield", "yield")) %>%
  .[, variable := case_when(
    variable == "det_yield" ~ "Yield",
    variable == "yield" ~ "Yield including errors"
  )] %>%
  .[, group := case_when(
    group == 0.01 ~ "site 1",
    group == 0.25 ~ "site 2",
    group == 0.5 ~ "site 3",
    group == 0.75 ~ "site 4",
    group == 0.99 ~ "site 5"
  )]

# /*--------------------------------*/
#' ## Visualization
# /*--------------------------------*/
sub_dt <- res_y_dt[variable == "Yield" & N == opt_N]

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.title = element_blank()) +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))
```

@@

```{r prepare-data-vis, cache = TRUE}
# /*===========================================*/
#' =  Prepare illustrative yield response curve estimated by RF =
# /*===========================================*/

# /*--------------------------------*/
#' ## Preparation
# /*--------------------------------*/
# --- ML functions --- #
library(grf)
source(here("GitControlled/Codes/0_2_functions_main_sim.R"))

@@

# /*===== Train ML =====*/
temp_var_ls <-
  c(
    "alpha1", "alpha2", "beta1", "beta2", "ymax1",
    "ymax2", "theta_1", "theta_2"
  )

@@

# === Yield prediction === #
# --- All N experimental rates --- #
N_rate <- test_dt[, aa_n] %>%
  unique() %>%
  sort()
# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
tg_N_rate <- N_rate[c(2, 3, 4)]

# --- for true yield response function --- #
seq_N <-
  seq(min(N_rate) - 30, max(N_rate) + 30, by = 1)
# seq_N <-
#   seq(min(N_rate), max(N_rate), by=1)

res_true <-
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = unique_subplot_id] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield * (1 + m_error)]

# --- for predicted yield at five experimental N rates --- #
res_pred <-
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)), ] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  .[, RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[, BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))

find_examples_main <-
  res_pred %>%
  .[variable == "BRF" & aa_n == N, ] %>%
  .[, y_diff_brf := abs(yield - value)] %>%
  .[y_diff_brf < 500, unique_subplot_id]
# .[y_diff_brf < 500 & y_diff_brf < 1000, unique_subplot_id]

@@

vis_res_true <-
  res_true[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[, site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
  )]

vis_res_pred <-
  res_pred[unique_subplot_id %in% c("2_18", "6_47")] %>%
  .[, site := case_when(
    unique_subplot_id == "2_18" ~ "site 1",
    unique_subplot_id == "6_47" ~ "site 2"
  )] %>%
  .[, type := "Predicted"] %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed Rate",
    "Unobserved Rate"
  )] %>%
  setnames("variable", "model") %>%
  .[, .(N, value, type, observed, model, site)]

vis_true_points <-
  vis_res_true[N %in% unique(vis_res_pred$N), ] %>%
  .[, type := "True"] %>%
  .[, observed := ifelse(
    aa_n == N,
    "Observed Rate",
    "Unobserved Rate"
  )] %>%
  setnames("yield", "value") %>%
  .[rep(1:.N, 2), ] %>%
  .[, model := c("RF", "BRF") %>% rep(each = 10)] %>%
  .[, .(N, value, type, observed, model, site)]

vis_all_points <- rbind(vis_res_pred, vis_true_points)
```

```{r make-plot-MB-BRF-y}
vis_MB_BRF_y <-
  ggplot() +
  # --- true yield response curve --- #
  geom_line(
    data = vis_res_true,
    aes(x = N, y = yield, group = site)
  ) +
  geom_point(
    data = vis_all_points,
    aes(y = value, x = N, color = observed, shape = type),
    size = 2
  ) +
  geom_line(
    data = vis_all_points[type == "Predicted", ],
    aes(y = value, x = N, color = site),
    linetype = 2,
    size = 0.5
  ) +
  geom_vline(
    xintercept = vis_res_true$aa_n %>% unique(),
    color = "red",
    linetype = 2,
    size = 0.3
  ) +
  annotate(
    "text",
    x = 180,  y = 9400,
    label = "Observed Rate \n = 150 (kg/ha)",
    family = "Times",
    size = 3
  ) +
  scale_shape_manual(
    values = c("Predicted" = 2, "True" = 16),
    name = "Yield Type"
  ) +
  scale_color_manual(
    values = c(
      "Observed Rate" = "red",
      "Unobserved Rate" = "blue"
    ),
    name = ""
  ) +
  facet_grid(. ~ model) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  guides(color = "none") +
  theme_dist
```

@@

```{r}
variogram_tb <-
  data.frame(
    Parameters = c("alpha_ij", "beta_ij", "ymax_ij", "varepsilon_ij"),
    Range = c(400, 400, 400, 400),
    Mean = c(-0.5, format(0), 12000, format(0)),
    Nugget = format(c(0, 0, 0, 0)),
    Sill = c(0.02, format(1, nsmall = 1), 2000000, 0.015)
  ) %>%
  flextable() %>%
  compose(i = 1, j = 1, part = "body", value = as_paragraph(as_i("\U03B1"), as_sub(as_i("i,j")))) %>%
  compose(i = 2, j = 1, part = "body", value = as_paragraph(as_i("\U03B2"), as_sub(as_i("i,j")))) %>%
  compose(i = 3, j = 1, part = "body", value = as_paragraph(as_i("ymax"), as_sub(as_i("i,j")))) %>%
  compose(i = 4, j = 1, part = "body", value = as_paragraph(as_i("\U03B5"), as_sub(as_i("i,j")))) %>%
  compose(i = 1, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("-2"))) %>%
  compose(i = 3, j = 3, part = "body", value = as_paragraph("1.2", "\U2A2F", "10", as_sup("4"))) %>%
  compose(i = 3, j = 5, part = "body", value = as_paragraph("2.0", "\U2A2F", "10", as_sup("6"))) %>%
  compose(i = 4, j = 5, part = "body", value = as_paragraph("1.5", "\U2A2F", "10", as_sup("-2"))) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # --- change headers labels--- #
  set_header_labels(values = list(
    Parameters = "Parameters",
    Range = "Range (m)",
    Mean = "Mean",
    Nugget = "Nugget",
    Sill = "Sill"
  )) %>%
  #- change the borders just for consistency with other tables -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  footnote(
    value = as_paragraph("NOTE: Only in ", as_i("ymax"), " are consistent units of measurement used for Mean, Nugget, and Sill ", "(", as_i("kg"), ")."),
    ref_symbols = NA
  ) %>%
  # set_caption(
  #   caption = "Table C.1: The parameters for the Variogram models",
  #   style = "Table Caption"
  # ) %>%
  autofit()
```

@@

one_subplot <- ex_subplots[3, ]

@@

#-- (2) create a map of subplots in a plot --##
subplots_inPlot <-
  ggplot() +
  geom_sf(data = ex_plot, fill = "green") +
  geom_sf(data = ex_subplots, fill = NA, size = 1) +
  geom_sf(data = ex_subplots[2, ], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("4 \u00D7 1 subplots") +
  theme_figure

@@

#-- (3) create a map of cells in a subplot --#
cells_inSubplot <-
  ggplot() +
  geom_sf(data = ex_one_subplot, fill = "green", size = 1) +
  geom_sf(data = ex_cells, fill = NA) +
  geom_sf(data = ex_cells[2, ], fill = "skyblue", size = 1) +
  coord_sf(expand = FALSE) +
  # theme_void() +
  ggtitle("6 \u00D7 6 cells") +
  theme_figure

@@

#-- (4)put them on the same map --#
field_structure <-
  ggplot() +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  # /*----------------------------------*/
  #' ##  base maps
  # /*----------------------------------*/
  # --- plot level --- #
  annotation_custom(grob_plot,
    xmin = 0, xmax = 0.4, ymin = 0, ymax = 1
  ) +
  # --- subplot level --- #
  annotation_custom(grob_subplots_inPlot,
    xmin = 0.565, xmax = 0.665, ymin = 0.35, ymax = 0.7
  ) +
  # --- cell level --- #
  annotation_custom(grob_cells_inSubplot,
    xmin = 0.8, xmax = 0.8 + 0.2, ymin = 0.382, ymax = 0.382 + 0.2
  ) +
  # /*----------------------------------*/
  #' ## Add braces
  # /*----------------------------------*/
  # --- between plot and subplot --- #
  geom_brace(aes(c(0.43, 0.43 + 0.1), c(0.372 - 0.004, 0.645 + 0.013)), color = "red", rotate = 270, inherit.data = F) +
  # --- between subplot and cell --- #
  geom_brace(aes(c(0.68, 0.68 + 0.1), c(0.401 - 0.002, 0.529 + 0.011)), color = "red", rotate = 270, inherit.data = F) +
  # /*----------------------------------*/
  #' ## add annotations
  # /*----------------------------------*/
  # --- annotation for plot --- #
  geom_segment(aes(x = 0.42, xend = 0.383, y = 0.60, yend = 0.52),
    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
  ) +
  annotate("text", x = 0.42 + 0.015, y = 0.60 + 0.02, label = "plot", family = "Times New Roman") +
  # --- annotation for subplot --- #
  geom_segment(aes(x = 0.7, xend = 0.64, y = 0.37, yend = 0.45),
    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
  ) +
  annotate("text", x = 0.7 + 0.035, y = 0.37 - 0.01, label = "subplot", , family = "Times New Roman") +
  # --- annotation for cell --- #
  geom_segment(aes(x = 0.9, xend = 0.87, y = 0.365, yend = 0.41),
    arrow = arrow(length = unit(0.1, "cm")), size = 0.5
  ) +
  annotate("text", x = 0.9 + 0.02, y = 0.365 - 0.005, label = "cell", , family = "Times New Roman") +
  theme_void()
```

@@

```{r, dependson = "setup"}
# === alpha map === #
field_alpha <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = alpha), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(1) " ~ alpha)) +
  theme(legend.title = element_blank()) +
  theme_figure

# === beta map === #
field_beta <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = beta), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression("(2) " ~ beta)) +
  theme(legend.title = element_blank()) +
  theme_figure

@@

# === m_error map === #
field_m_error <-
  ggplot(field_cell_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  ggtitle(expression(paste("(4) " ~ epsilon, " (kg/ha)"))) +
  theme(legend.title = element_blank()) +
  theme_figure

@@

```{r}
vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% c(10, 20, 30) & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  guides(
    fill = guide_legend(override.aes = list(shape = 21))
  ) +
  labs(fill = "Simulation Round", shape = "Method") +
  # guides(fill = "none") +
  # facet_wrap( ~ Model, ncol = 2) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist
```

@@

# === Function for RMSE Calculation === #
rmse_general <- function(preds, actual) {
  sqrt(mean((actual - preds)^2)) %>%
    round(., 1) %>%
    format(, nsmall = 1)
}

rmse <- sample_simRes_test_y %>%
  .[, .(
    rmse_y_det = rmse_general(pred_yield, det_yield),
    rmse_y = rmse_general(pred_yield, yield)
  ), by = .(Method, Model)]

rmse <- sample_simRes_test_y %>%
  .[, .(
    rmse_y_det = paste0("RMSE = ", rmse_general(pred_yield, det_yield)),
    rmse_y = paste0("RMSE = ", rmse_general(pred_yield, yield))
  ), by = .(Method, Model)]

vis_y_pred <- ggplot(sample_simRes_test_y) +
  geom_point(aes(x = det_yield, y = pred_yield), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  geom_text(
    data = rmse, aes(x = -Inf, y = +Inf, label = rmse_y_det),
    hjust = -0.1, vjust = 3, size = 3.5, family = "Times New Roman"
  ) +
  facet_grid(Model ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Predicted Yield (kg/ha)") +
  labs(x = "True Yield without error (kg/ha)") +
  theme_dist
```

@@

```{r, dependson = "source-results"}
# /*----------------------------------*/
#' ## Distribution of RMSE of EONR estimates
# /*----------------------------------*/
plot_dis_optN <-
  allML_summary_bySim %>%
  .[type == "test", ] %>%
  # .[Method %in% c("RF", "BRF", "CF_base"), ] %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = rmse_optN, fill = Method), alpha = 0.7) +
  facet_wrap(~Model, ncol = 1) +
  labs(x = "RMSE (kg/ha)") +
  theme_dist
